Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
nudge

\item We exploit a CEGIS-based approach, that uses inductive synthesis
in conjunction with a formal verification algorithm, for synthesising 
correct-by-design robust digital controllers for non-fragile closed-loop 
stability.

\item Experiments obtained with our synthesiser show that the combination 
of interval arithmetic to represent the controller coefficients and a two-stage 
verification approach to continuously refine precision, we are able to compute 
a parametric sound solution for $14$ out of $15$ digital stabilizing controllers 
given a set of continuous and discrete plant with parametric uncertainties.

>>>>

\item We exploit a CEGIS-based approach that uses inductive synthesis
together with a bit-precise formal verification algorithm for synthesising
correct-by-design robust digital controllers for non-fragile closed-loop
stability.

\item Experiments obtained with our synthesiser show that the combination of
interval arithmetic to represent the controller coefficients and a two-stage
verification approach to continuously refine precision enables us to compute
a parametric, sound solution for $14$ out of $15$ digital stabilizing
controllers for a set of continuous and discrete plants with parametric
uncertainties.
